---
title: "R_Package_Leow"
author: "ChiJingLeow"
date: "12/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation

Load in these libraries.
```{r}
library(ggplot2)
library(tidyverse)
```

You might need to install these R packages for this package to run.
```{r eval=FALSE}
install.packages("edgeR")
install.packages("limma")
library("edgeR")
library("limma")
```

Now you can install my R package!
and load it...
```{r}
devtools::install_github("ChiJingLeow/R_Package_Leow")
library("R_Package_Leow")
```

Download the data for this package. 
The first file is the gene counts data.
The second file is the sample information.
```{r}
download.file("https://raw.githubusercontent.com/ChiJingLeow/R_Package_Leow/master/Data/GSE60450_LactationGenewiseCounts.txt", destfile = "cloud/project/Data/Genedata.txt")

download.file("https://github.com/ChiJingLeow/R_Package_Leow/blob/master/Data/SampleInfo_Corrected.txt", destfile = "cloud/project/Data/Sampleinfo.txt")
```



an example of each function and how it works.
description about why this is a good function. 
expected output.